Comparison among doublet predictions on benchmarking datasets

### 2024-06-03 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
add section with metrics

>>>>

## Performance metrics

This section shows performance metrics for the consensus calls for each dataset.

```{r}
doublet_df_list |>
  purrr::iwalk( 
    \(df, dataset) {
        print(glue::glue("======================== {dataset} ========================"))

        cat("Table of consensus calls:")
        print(table(df$consensus_call))

        cat("\n\n")

        caret::confusionMatrix(
          # truth should be first
          table(
            "Truth" = df$ground_truth,
            "Consensus prediction" = df$consensus_call
          ), 
          positive = "doublet"
        ) |>
        print()
    }
  )
```
